Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-07-30 sections/approach.tex
Move limitation described in approach section to discussion

% Our proposed approach is empirically driven and automatically adjusts to the quality the data.
While our proposed approach is straightforward, empirically driven, and automatically adjusts to the quality of the data, it has a few drawbacks.
First, we have to accept that some comments cannot be reliably or confidently classified.
We denote these as \emph{undetermined} to differentiate them from comments whose usefulness is \emph{unclear} (i.e. cannot be assessed subjectively).
Secondly, owing to the subjective assessment of usefulness, this representation fundamentally implies supervised classification requiring nontrivial training data to define representative classification sets.
This limits the practicality of application to projects with a large enough number of comments, where the classification effort saved overcomes the training costs.

>>>>

% Our proposed approach is empirically driven and automatically adjusts to the quality the data.
While our proposed approach is straightforward, empirically driven, and automatically adjusts to the quality of the data, it has a few drawbacks.
We have to accept that some comments cannot be reliably or confidently classified.
We denote these as \emph{undetermined} to differentiate them from comments whose usefulness is \emph{unclear} (i.e. cannot be assessed subjectively).
Secondly, owing to the subjective assessment of usefulness, this representation fundamentally implies supervised classification requiring nontrivial training data to define representative classification sets.
